Demonstration of matching route networks

### 2024-01-26 demo.qmd
Update with osm ids

```{r}
rnet_x = rnet_x_projected
rnet_y = rnet_y_projected
distance = 9
dist_chop = 0.1
rnet_join = function(
    rnet_x,
    rnet_y,
    distance = 9,
    dist_chop = 0.1
    ) {
  # Check CRS is projected:
  stopifnot(
    sf::st_is_longlat(rnet_x) == FALSE,
    sf::st_is_longlat(rnet_y) == FALSE
  )
  rnet_x_geos = geos::as_geos_geometry(rnet_x)
  rnet_y_geos = geos::as_geos_geometry(rnet_y)
  params = geos::geos_buffer_params(end_cap_style = "flat")
  rnet_x_buffer = geos::geos_buffer(rnet_x_geos, distance, params = params)
  rnet_xbl = geos::geos_boundary(rnet_x_buffer)
  rnet_xblb = geos::geos_buffer(rnet_xbl, dist_chop, params = params)
  rnet_xlbc = geos::geos_make_collection(rnet_xblb)
  rnet_xlbcu = geos::geos_unary_union(rnet_xlbc)
  rnet_y_chopped = geos::geos_difference(
    rnet_y_geos,
    rnet_xlbcu
  )
  rnet_ycj = geos::geos_inner_join_keys(
    rnet_y_chopped,
    rnet_x_buffer
  )
  rnet_y_df = sf::st_drop_geometry(rnet_y)
  rnet_y_df_expanded = rnet_y_df[rnet_ycj$x, ]
  rnet_y_df_expanded$id_x = rnet_x_df[[1]][rnet_ycj$y]
  # Replace 'id_x' with the name of the first column in rnet_x_df:
  nx = which(names(rnet_y_df_expanded) == "id_x")
  new_name = names(rnet_x_df)[1]
  names(rnet_y_df_expanded)[nx] = new_name
  rnet_y_df_expanded
}
# Test it:
rnet_join(rnet_x, rnet_y)
```

>>>>

```{r}
rnet_x = rnet_x_projected
rnet_y = rnet_y_projected
distance = 9
dist_chop = 0.1
rnet_join = function(
    rnet_x,
    rnet_y,
    distance = 9,
    dist_chop = 0.1
    ) {
  # Check CRS is projected:
  stopifnot(
    sf::st_is_longlat(rnet_x) == FALSE,
    sf::st_is_longlat(rnet_y) == FALSE
  )
  rnet_x_geos = geos::as_geos_geometry(rnet_x)
  rnet_y_geos = geos::as_geos_geometry(rnet_y)
  params = geos::geos_buffer_params(end_cap_style = "flat")
  rnet_x_buffer = geos::geos_buffer(rnet_x_geos, distance, params = params)
  rnet_xbl = geos::geos_boundary(rnet_x_buffer)
  rnet_xblb = geos::geos_buffer(rnet_xbl, dist_chop, params = params)
  rnet_xlbc = geos::geos_make_collection(rnet_xblb)
  rnet_xlbcu = geos::geos_unary_union(rnet_xlbc)
  rnet_y_chopped = geos::geos_difference(
    rnet_y_geos,
    rnet_xlbcu
  )
  rnet_ycj = geos::geos_inner_join_keys(
    rnet_y_chopped,
    rnet_x_buffer
  )
  rnet_y_df = sf::st_drop_geometry(rnet_y)
  rnet_y_df_expanded = rnet_y_df[rnet_ycj$x, ]
  rnet_y_df_expanded$id_x = rnet_x_df[[1]][rnet_ycj$y]
  # Replace 'id_x' with the name of the first column in rnet_x_df:
  nx = which(names(rnet_y_df_expanded) == "id_x")
  new_name = names(rnet_x_df)[1]
  names(rnet_y_df_expanded)[nx] = new_name
  rnet_y_df_expanded
}
# Test it:
res = rnet_join(rnet_x, rnet_y)
res
res |>
  dplyr::group_by(id) |>
  dplyr::summarise(
    osm_ids = paste(osm_id, collapse = ", ")
  )

```
